Temperature Measurements in Optical Tweezer Experiments

### 2016-08-08 doc/draft1.tex
good things going on
**changed the particle tracker, so it prints out energies as well
**changed particle class, so mass and potential energy is included
**changed calculation of forces, so that potential energy is included

**added bib file for references
**outlined structure of thesis
Added tests for single particle investigation
Radical changes!
preparation for the remodeling of the program, such that
many configurations can be investigated and saved
running through parameters
does not work yet. run gets stuck and does not do much...

\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{a4paper}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{hyperref} % verlinkungen
\usepackage{textcomp}
\usepackage{flafter}
\usepackage{booktabs}
\usepackage{array}
\usepackage{paralist}
\usepackage{dsfont}
\usepackage{color}
\usepackage{bbold}
\usepackage{float}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{subcaption}
\usepackage{fancyhdr}
\setlength{\headheight}{15.2pt}
\pagestyle{fancy}
\usepackage{listings} 
\usepackage{pict2e}
\usepackage{xfrac}
\usepackage{german}
\usepackage{mathtools}
\usepackage{graphicx}

@@

\begin{document}
\title{Monte-Carlo Simulation von TIP5P-Wasser}
\author{Mathias H"old, Theodor Adaktylos}
\date{Wintersemester 2015/2016}
\maketitle
\thispagestyle{empty}
\newpage
\section{Introduction}

>>>>

\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{a4paper}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{hyperref} % verlinkungen
\usepackage{textcomp}
\usepackage{flafter}
\usepackage{booktabs}
\usepackage{array}
\usepackage{paralist}
\usepackage{dsfont}
\usepackage{color}
\usepackage{bbold}
\usepackage{float}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{subcaption}
\usepackage{fancyhdr}
\setlength{\headheight}{15.2pt}
\pagestyle{fancy}
\usepackage{listings} 
\usepackage{pict2e}
\usepackage{xfrac}
\usepackage[english]{babel}
\usepackage{mathtools}
\usepackage{graphicx}

@@

\begin{document}
\title{Temperature Measurements in Optical Tweezer Experiments}
\author{Mathias H\"old, BSc.}
\date{2016}
\maketitle
\thispagestyle{empty}
\newpage
\section{Introduction}
%something about computer science in general, optical tweezers and the need to study the
%systems on computers yada yada

\newpage
\section{Motivation}
%introduction of the experiment, the problem and the idea

\newpage
\section{Simulation}
%simulation techniques and general concept of the simulation itself, used methods and so on 
To study the problem on the computer, one needs certain techniques. These techniques and their application will be described in this section.

\subsection{Molecular Dynamics}

\subsection{Reduced Units}
\subsection{The Glass Nanoparticle}
The glass particle from the experiment will be represented by a system of particles, interacting via a Lennard-Jones potential of the form
\begin{equation}
    U(r) = 4\varepsilon\left[\left(\frac\sigma r\right)^{12} - \left(\frac\sigma r\right)^6\right]
\end{equation}
or, using reduced units:
\begin{equation}
    U(r^*) = 4\left[{r^*}^{-12} - {r^*}^{-6}\right]
\end{equation}

\newpage
\section{Results}
% results with different parameters, graphs, etc.

\newpage
\section{Conclusion}
% what does this all tell us? do we need to study more of this?

\newpage
\bibliography{references}
\bibliographystyle{plain}
